\documentclass {article}
\usepackage{amssymb}
\begin {document}
\title{\textbf{Laboratory Data Management System}}
\author{Harshit Maheshwari\\N V Subba Rao\\[0.5cm]
\small{under the guidance of}\\ Prof. T.V. Prabhakar}
\date{August 23, 2013}
\maketitle
\newpage
%\tableofcontents
\newpage
%\section {Answer 1}
%\subsection{(a)}
\flushleft{
\LARGE{\textbf{User Stories}}\\[0.5cm]
\normalsize{
The users of the Laboratory Data Management System will consist of the following roles:
\begin{itemize}
	\item Researcher
	\item Principal Investigator(PI)
	\item Administrator
\end{itemize}
We have collected the following user stories\footnotemark[1]:
\begin{enumerate}
	\item As a laboratory researcher, since security is a primary concern, the credentials of the user should be verified before he accesses the system. 
	\item As a user, for ease of access, I would like to have:
		\begin{itemize}
			\item \textbf{User Generic Tab:} Common data/protocols that can be viewed or modified by anyone.
			\item \textbf{User Specific Tab:} The data here can be modified only by the owner.
		\end{itemize}
	\item All the content present in the system should be readable by all and can be searched with the following options:
		\begin{itemize}
			\item Search by researcher/experimenter's name 
			\item Search by experiment name or experiment id
			\item Search by keywords in the experiment 
		\end{itemize}
		The above search criteria can be used for searching entire articles or only images. 
	\item As a researcher, I would like to have exclusive permission to modify the data added by me. 
	\item As a researcher, I would like to ensure that all the revisions/edits made by any researcher should have associated timestamps to maintain the integrity of the data. 
	\item As a Principal Investigator, I want the privilege to approve or disapprove the data collected, modifications made to the protocols\footnotemark[2] or notes added to the protocols by lab researchers. 
	\item As an administrator I want the permission to create or delete accounts of users in the system. 
\end{enumerate}
\footnotetext[1]{We have used the \textbf{INVEST} model to ensure that all the user stories are independent, negotiable, valuable, estimable, small and testable }
\footnotetext[2]{A protocol is a standard procedure prescribed to carry out an experiment.}
}}


\end{document}

